Super-awesome paper with super-cool results

### 2021-11-17 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
added a skeleton to the proposed paper
hs: small edits

\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath]{revtex4-1}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[dvipsnames]{xcolor}
\usepackage{bm}
\usepackage{times}
\usepackage{xspace}
\usepackage[varg]{txfonts}
\usepackage[normalem]{ulem} % To get strikethrough (\sout)
\usepackage[colorlinks]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{url}
\usepackage{float}
\usepackage[bottom]{footmisc}
\usepackage{lineno}
%\linenumbers
\usepackage{makecell}

@@

\newcommand{\AEI}{\affiliation{Max Planck Institute for Gravitational Physics (Albert Einstein Institute), Am M\"uhlenberg 1, Potsdam 14476, Germany}}
\newcommand{\UMD}{\affiliation{Department of Physics, University of Maryland, College Park, MD 20742, USA}}

@@

\author{TBD}

@@

%%%%%%%%%%%%%%%%%
\section{Method}
\label{sec:method}
%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
\label{sec:acknowledgements}
%%%%%%%%%%%%%%%%%

>>>>

\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath]{revtex4-1}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[dvipsnames]{xcolor}
\usepackage{bm}
\usepackage{times}
% \usepackage[varg]{txfonts}
\usepackage{txfonts}
\usepackage{xspace}
\usepackage[normalem]{ulem} % To get strikethrough (\sout)
\usepackage[colorlinks]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{url}
\usepackage{float}
\usepackage[bottom]{footmisc}
\usepackage{lineno}
%\linenumbers
\usepackage{makecell}
\usepackage{microtype}

@@

\newcommand{\pd}{\partial}
\newcommand{\dd}{{\rm d}}
\newcommand{\dV}{{\rm d}^{4}x \, \sqrt{-g} \,}
\newcommand{\lame}{\lambda_{\rm e}}
\newcommand{\lamo}{\lambda_{\rm o}}

% Comment commands
\newcommand{\ag}[1]{{\textcolor{cyan}{{[AG: #1]}} }}
\newcommand{\hs}[1]{{\textcolor{blue}{{[HS: #1]}} }}
\newcommand{\ab}[1]{{\textcolor{green}{{[AB: #1]}} }}

\newcommand{\AEI}{\affiliation{Max Planck Institute for Gravitational Physics (Albert Einstein Institute), Am M\"uhlenberg 1, Potsdam 14476, Germany}}
\newcommand{\UMD}{\affiliation{Department of Physics, University of Maryland, College Park, Maryland 20742, USA}}

@@

\author{Abhirup Ghosh}
\author{Hector O. Silva}
\AEI
\author{Alessandra Buonanno}
\AEI
\UMD

@@

%%%%%%%%%%%%%%%%%
\section{Methods}
\label{sec:method}

\subsection{The parametrized waveform model}
\label{sec:review_pSEOB}

\subsection{The parametrized ringdown spin expansion coefficients}
\label{sec:review_parspec}

\subsection{Overview of modified gravity theories}
\label{sec:review_theories}

A broad class modified gravity theories are capture by the action
%
\begin{align}
S &= \frac{1}{16 \pi G} \int \dd^4x \sqrt{-g}
\left[ R + \dots \right.
\nonumber \\
&\quad
\left.
\right]
\end{align}
%

\begin{table}[t]
\begin{tabular}{c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega$ & $\delta \tau$ & Refs. \\
\hline
\dots & \dots & \dots & \dots & \dots \\
\hline
\hline
\end{tabular}
\caption{Summary of theories consider in this paper.
\hs{Add a column with the constraint (if any) that we placed.}}
\label{tab:ref_stars}
\end{table}

%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}
%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
\label{sec:acknowledgements}
%
We thank Emanuele Berti and Andrea Maselli for discussions.
%
The authors are grateful for the computational resources provided by the AEI,
specifically the {\sc Hypatia} cluster.
%
The authors would like to thank everyone at the frontline of the Covid-19
pandemic.
%%%%%%%%%%%%%%%%%
